\chapter{Introduction}
\label{chap:introduction}

\section{Scope}

This user manual will explain you how to use our software efficiently. It will
show you how the different sensors interact with each other and how statistics
are used to schedule tasks. It will also show you how you can properly interact
with the software. It will be useful reference material during the use of the
Software. This document will not show you how to integrate the software in your
specific environment. Thus not showing you how to create and implement databases
nor does it show you how to care for the different plants. This document wills
also not show you how to properly install the sensors.


\section{Purpose}

This document defines all essential information for the user to use the software application. 
The system functions are shown step by step for the user. In case of a
\textbf{\emph{\glspl{crisis}}} the user can look up in this file with the
given error code which action has to be taken accordingly.
In addition the definition of different icons will be shown and explained.


\section{Intended audience}

The software is intended to be primarily used in the enterprise sector more
specially the agriculture sector. The manual  will help the people concerned
with operating the software correctly. The gardener can use this document to
understand how he can interact with the system and retrieve information about
the inventory. The manager can learn how to add tasks to the schedule correctly,
how to access camera. The technician will know where to look for problems with
the sensors as well as what alerts he can expect. The gardener and the
technician can find information about the schedule and what task can be given to
the respecting personnel.

\section{\mysystemname}

The software is used in agriculture/gardening that means planting and harvesting
plants. The main purpose is to do so in the most efficient way by using
different hardware like sensors. Basically the software allows the user to check
if the soil needs nutrition or water to allow for a optimal growing of the
plants. Also the software gives tasks to the gardner so that no mistakes are
made by the individual human. The software creates statistics with the data
gather by the sensors about the plants and their environment. The software gives
insight to the results achieved with varying environmental conditions.


\subsection{Actors \& Functionalities}

The \textbf{gardener} is in charge of planting and retrieving the plants. The
gardner uses other actors like the ph meter and the ec meter to check the water
or the soil of the diffrent plants.Furthermore he sees two tables the
sensors table with their data and the storage of the crops.He can take
away crops but not delete them from the list. Also he has the possibility
to ask for a diffrent food or vegtable which isn't in the table. For
planting the plants he sees the temperature preference and the ph-Amount
and he has to deside in which room he has to plant the given crops.\break

\noindent The \textbf{technician} sees the tables of sensors and has to
check if there is a sensor which isn't functionaing properly. If he sees
that a sensors gives a non realistic value inside the table he can request
a new sensor to the manager by filling difrent input fields. In addition
he can also add a new sensor to the list and delete one in case the sensor
isn't util or functional any more for on ore several reason.\break

\noindent The \textbf{manager} sees 4 tables. One keeps track of the
inventory of the diffrent crops left or available. Also he sees when the
gardener retrives crops with the indicated date. He's the only person who
can delete from the inventory. In addition, he can also insert new
vegtables or fruits inside the inventory table. He has to implent the data
correctly that means the ph-Amount and temperature reaserches have to be
done by him self. Furthermore he sees any request for vegtables, frood or
sensors. He has the right to decline or accept it.\break

\noindent The \textbf{director} can basically do everything what the
other actors can like the manager technician and gardner. In addtion, he
gets the statistics of the month which means he gets displayed diffrent
information like how mony crops have been used how many times where the
leds on and what are the diffrent costs for it.\break

\noindent The non human Actors:\hfill \break
The \textbf{temperature sensor} is in charge to read the temperature and to
communicate the data to the computer.

\noindent The \textbf{Software} is in charge to commit any request from human
actors to the respected person. In addtion if the gardner doesn't asks for a
request the software will ask for it automatically. In addtions, the soft keeps
track of the retriving crops and send the information to the manager.

\noindent The \textbf{humidity sensor} is in charge to collect the humidity
percentage in the soil and communicate it to the computer.

\noindent The \textbf{light sensor} is in charge to collect the light density
 inside and outside the greenhouse and to communicate the data to the
 computer.

\noindent The \textbf{motion sensor} is  in charge of the security of the
greenhouse. The sensors captures any motion by human or inhuman to the
computer.


\noindent The \textbf{ph meter} is used to check if the water has the perfect ph
scale for the plants and has to communicate the data to the computer.

\noindent The \textbf{Ec meter} is in charge the check if the nutrition inside
the water tank is good.

\noindent The \textbf{security camera} is recording what is happening inside the
greenhouse which is displayed in live on the website.

\noindent The mouse and keyboard are used to control and give input to the
computer and the web page.

\noindent The display is there to display the data webside and so on. 

\noindent The heater is used to warm up the different rooms to a given
temperature.

\noindent The windows can automatically be opened to give fresh air and cool
down the temperature.


\subsection{Operating environment}
Brief overview of the infrastructure on which the software is deployed and used.
Controlling part of the software will run on a windows 10 Pro environment while
created statistics will be stored in a SQL database. Data from the sensors will
also be stored in a SQL database. The website can be accessed from a
phone/tablet or computer. Windows 10 is used for its GUI so it is easier to use
for the people using the software.

\section{Document structure}  
Information on how this document is organised and it is expected to be
used. Recommendations on which members of the audience
should consult which sections of the document, and explanations about the used
notation (i.e. description of formats and conventions) must also be provided.
