\subsubsection{subfunction-sfAcceptRequestForNewSensor}

\label{RE-use-case-sfAcceptRequestForNewSensor}


The manager can accept a request from the technician for a sensor. The expedition happens on the request sensor
table on the request screen from the manager. The manager accepts the request and the system tells the technician that he can now replace the sensor.		  


\begin{usecase}
  \addheading{Use-Case Description}
  \addsingletwocolumnrow{Name}{sfAcceptRequestForNewSensor}
  \addsingletwocolumnrow{Scope}{system}
  \addsingletwocolumnrow{Level}{subfunction}
  

\addrowheading{Primary actor(s)}
\addnumberedsinglerow{}{\msrcode{actManager[active]}}



\addrowheading{Goal(s) description}
\addsinglerow{The manager can accept a request from the technician for a sensor. The expedition happens on the request sensor
table on the request screen from the manager. The manager accepts the request and the system tells the technician that he can now replace the sensor.}

\addrowheading{Protocol condition(s)}
\addnumberedsinglerow{}{
The system is booted up and the manager needs to be on the request screen and there needs to be an available request for a sensor.
}

\addrowheading{Pre-condition(s)}
\addnumberedsinglerow{}{
none
}

\addrowheading{Main post-condition(s)}
\addnumberedsinglerow{}{
The system inserts the value to the sensor accepted table from the technician.
}

\addrowheading{Additional Information}
\addsinglerow{
In case of a decline no action happens that means no value added to the accepted sensor table from the technician.
}

\end{usecase} 

